Namespace Tunnels in Content-Centric Networks

### 2017-04-09 paper/01-introduction.tex
Chris's pass

\section{Introduction}
Content-centric networking (CCN) is a type of request-based information-centric
networking (ICN) architecture. In CCN, all data is named. Consumers obtain data
by issuing an explicit request for the content by its name. The network is
responsible for forwarding this request towards producers, based on the name,
who then generate and return the content response. Since a name uniquely identifies
a content response, routers may cache these packets to use in response to
future requests for the same name. As a consequence, all content has an (implicit
or explicit) authenticator that is used to verify the name-to-data binding. In
order to prevent cache poisoning attachs, wherein a malicious producer supplies
fake data in a content response that is propogated in the network, a router
should never serve (a) content with an invalid authenticator or (b) cached
content that it cannot verify. To enable (b), content objects with a digital
signature are expected to carry the public verification key or certificate. If the
authenticator is a MAC, then intermediate routers cannot verify it and should
therefore not cache the content.

One negative side effect of name-based requests is that any on-path or
eavesdropping adversary between a consumer and producer can learn the identity
and contents of all data in transit. In traditional IP-based networks, there are
generally two types of mechanisms to solve this problem: (1) anonymity
networks such as Tor \cite{tor} or (2) VPNs. As tools focused on anonymity,
the former help prevent linkability of packets to their requestors without
always protecting the identities or content themselves. In contrast, VPNs focus
on packet confidentiality by creating a tunnel between two private networks
or a consumer and single private network. All traffic over this tunnel is
encrypted and thereby opaque to an eavesdropper. VPNs differ from anonymity
networks such as Tor in that they are \emph{network-layer} mechanisms that
typically only introduces a single layer of encryption to protect traffic.
Thus, while Tor can be used to enable VPN-like functionality, it is often
far more inefficient since it operates above the network layer.

In ICN (or more specifically, CCN and NDN), ANDaNA was the first anonymity network of its
kind. Similar to Tor, ANDaNA uses circuits formed from anonymizing routers (ARs)
to marshall requests and responses between consumers and producers. The former
onion-encrypt interests and content using the public key(s) of the target ARs.
A variant of ANDaNA uses symmetric keys for packet encapsulation but suffers from
linkability. Tsudik et al. \cite{tsudik2016ac3n} proposed an optimized version of the symmetric-key
ANDaNA variant that did not permit linkability. To the best of our knowledge, there
is no anonymity network variant for ICN architectures. Though tunneling is only
useful for only a subset of ICN traffic, we believe it is a gap to be addressed
for this emerging technology, for a variety of reasons. {\bf First}, privacy
continues to be an elusive property for CCN applications. Tunneling will help
permit some degree of privacy within trusted AS domains from external passive
eavesdroppers. {\bf Second}, multi-hop circuits as used in ANDaNA are overkill
when trying to retain privacy instead of anonymity. {\bf Third}, end-to-end
sessions such as those enabled by CCNxKE \cite{ccnxke} and similar protocols
only serve those engaged in the session. In contrast, since the threat model is
different, tunneled traffic has the potential to serve any number of consumers
within the same trusted domain. Thus, while tunneling may contrast the content-centric
nature of data transmission in CCN, it fills a needed void for this architecture.

In this paper, we present CCVPN, a secure tunneling protocol and system design for
CCN. Similar to ANDaNA, CCVPN encrypts interests and content objects between producers
and consumers. In contrast, CCVPN only encrypts packets between a \emph{single}
source and destination to form a tunnel. In the standard configuration, both
endpoints of the tunnel are gateways between two trusted domains. It is possible,
however, for the source to be an individual consumer. In fact, the standard two-hop
ANDaNA circuit is identical to a nested tunnel with the same source. Thus,
CCVPN is more flexible than a general anonymity network.

>>>>

\section{Introduction}

Content-centric networking (CCN) is a type of request-based information-centric
networking (ICN) architecture. In CCN, all data is named. Consumers obtain data
by issuing an explicit request for the content by its name. The network is
responsible for forwarding this request towards producers, based on the name.
The producers then generate and return the content response. Since a name uniquely identifies
a content response, routers may cache content responses and use them to satisfy
future requests for the same name.
% Since content may be served from anywhere
% in the network, all content has an (implicit or explicit) authenticator that
% is used to verify the name-to-data binding. In
% order to prevent content poisoning attacks, wherein a malicious producer supplies
% fake data in a content response that is propagated in the network, a router
% should never serve (a) content with an invalid authenticator or (b) cached
% content that it cannot verify.

One negative side effect of name-based requests is that any on-path or
eavesdropping adversary between a consumer and producer can learn the identity
and contents of all data in transit. In traditional IP-based networks, there are
generally two mechanisms to solve this problem: (1) anonymity
networks, such as Tor \cite{dingledine2004tor}, and (2) VPNs. As tools focused on anonymity,
the former help prevent linkability of packets to their requesters without
always protecting the identities or content themselves. In contrast, VPNs focus
on packet confidentiality by creating a tunnel between two private networks
or between a consumer and a single private network. All traffic over this tunnel is
encrypted and opaque to an eavesdropper. VPNs differ from anonymity
networks such as Tor in that they are \emph{network-layer} mechanisms that
typically only introduce a single layer of encryption to protect traffic.
Thus, while Tor can be used to enable VPN-like functionality, it is often
far more inefficient since it operates above the network layer. Moreover,
Tor is often too heavy for the simple use case of protecting packets from
prying eyes.

ANDaNA \cite{dibenedetto2011andana} was the first anonymity network to address these
network-layer privacy concerns in CCN.
Similar to Tor, ANDaNA uses circuits composed of anonymizing routers (ARs)
to marshall requests and responses between consumers and producers. The former
onion-encrypt interests and content using the public key(s) of the target ARs.
A variant of ANDaNA uses symmetric keys for packet encapsulation but suffers from
linkability. Tsudik et al. \cite{tsudik2016ac3n} proposed an optimized version of
the symmetric-key ANDaNA variant that did not permit linkability. Still, neither of
these systems were designed to address the simple use case of a VPN: protecting
data that should only be revealed within a private network. Though tunneling CCN
traffic may only be useful for a subset of applications, we believe it is a gap to be addressed
for this emerging technology, for a variety of reasons. {\bf First}, privacy
continues to be an elusive property for CCN applications. Tunneling will help
permit some degree of privacy within trusted AS domains from external passive
eavesdroppers. {\bf Second}, multi-hop circuits as used in ANDaNA are overkill
when the goal is packet privacy instead of anonymity. {\bf Third}, end-to-end
sessions, such as those enabled by CCNxKE \cite{ccnxke} and similar protocols,
only serve those engaged in the session. In contrast, since VPNs operate at the
network layer, tunneled traffic has the potential to serve any number of consumers
within the same trusted domain. Thus, while tunneling may contrast the content-centric
nature of data transmission in CCN, it fills a void for this architecture.

In this paper, we present CCVPN, a secure tunneling protocol and system design for
CCN. Similar to ANDaNA, CCVPN encrypts interests and content objects between two endpoints.
However, in CCVPN, the endpoints are network gateways instead of ARs. In the standard configuration, both
endpoints of the tunnel are gateways between two trusted domains. Tunnels may
also be nested. Moreover, it is possible for the source to be an individual consumer.
In fact, the standard two-hop ANDaNA circuit is identical to a nested tunnel
with the same source. Thus, CCVPN is more flexible than a general anonymity network.
CCVPN is designed to use efficient symmetric-key cryptographic primitives, but it also
works with public-key algorithms when a proper key exchange or distribution mechansim
is absent. This makes it easy to deploy CCVPN in real-world CCN networks.

We design, implement, and evaluate CCVPN to gauge its perceived impact on normal
traffic. Our results indicate that the collective throughput across multiple
consumers sharing a tunnel remains stable up to a modest bound of $60$ consumers, each
requesting data at a rate of $1$ mbps. Moreover, as expected, the average RTT of
consumer requests decreases at a rate proportional to the collective throughput
and request rate. Further improvements in both throughput and perceived RTT
can be made with an implementation in a more performant CCN router, such as that of the CICN
project \cite{cicn}.

### 2017-04-09 paper/03-related.tex
Chris's pass

Content encryption seeks to solve the problem of data confidentiality rather than
privacy or anonymity. This technique allows content to be disseminated throughout
the network, since it cannot be decrypted by adversaries without the appropriate decryption key(s).
Many variations of this approach have been proposed based on general
group-based encryption \cite{Smetters2010}, broadcast encryption \cite{Misra2013,Ion2013}, and
proxy re-encryption \cite{Wood2014}. Kurihara et al. \cite{ifip15} generalized these specialized
approaches in a framework called CCN-AC, an encryption-based access control framework
that shows how to use manifests to explicitly specify and enforce other encryption-based
access control policies. Consumers use information in the manifest to (1) request appropriate
decryption keys and (2) use them to decrypt content object(s). The NDN NBAC \cite{yu2015name}
scheme is similar to \cite{ifip15} in that it allows decryption keys to be
flexibly specified by a data owner. However, it does this based on name engineering rules instead of
configuration. Interest-based access control \cite{ghali2015interest} is a different
type of access control scheme wherein content is optionally encrypted. Access
is protected by making the names of contents derivable only by authorized consumers.
NDN-ACE \cite{shangndn} is a recent access control framework for IoT environments
which includes a key exchange protocol for distributing secret keys to sensors.
All of these techniques, with few exceptions, use public-key cryptographic schemes
to protect only the \emph{payload} of content packets. They do not encapsulate complete
packets for private transmission between a source and sink domain. The exception is CCNxKE\cite{ccnxke}, 
which specifies a key exchange protocol that can bootstrap secure sessions between a source
a sink. CCNxKE can be used in CCVPN to establish pairwise shared secrets between tunnel
endpoints, even though this step is not strictly required.

>>>>

Content encryption seeks to solve the problem of data confidentiality rather than
privacy or anonymity. This technique allows content to be disseminated throughout
the network, since it cannot be decrypted by adversaries without the appropriate decryption key(s).
Many variations of this approach have been proposed based on general
group-based encryption \cite{Smetters2010}, broadcast encryption \cite{Misra2013,Ion2013}, and
proxy re-encryption \cite{Wood2014}. Kurihara et al. \cite{ifip15} generalized these specialized
approaches in a framework called CCN-AC, an encryption-based access control framework
that shows how to use manifests to explicitly specify and enforce other encryption-based
access control policies. Consumers use information in the manifest to (1) request appropriate
decryption keys and (2) use them to decrypt content object(s). The NDN NBAC \cite{yu2015name}
scheme is similar to \cite{ifip15} in that it allows decryption keys to be
flexibly specified by a data owner. However, it does this based on name engineering rules instead of
configuration. Interest-based access control \cite{ghali2015interest} is a different
type of access control scheme wherein content is optionally encrypted. Access
is protected by making the names of contents derivable only by authorized consumers.
NDN-ACE \cite{shangndn} is a recent access control framework for IoT environments
which includes a key exchange protocol for distributing secret keys to sensors.
All of these techniques, with few exceptions, use public-key cryptographic schemes
to protect only the \emph{payload} of content packets. They do not encapsulate complete
packets for private transmission between a source and sink domain. The exception is CCNxKE~\cite{ccnxke},
which specifies a key exchange protocol that can bootstrap secure sessions between a source
a sink. CCNxKE can be used by CCVPN to establish pairwise shared secrets between tunnel
endpoints, even though this step is not strictly required.

### 2017-04-09 paper/04-design.tex
new scripts for 1x1 and nxn
some results on n x n
Updates
done w/ writting
Chris's pass

\section{CCVPN}\label{metho}

Traditional Virtual Private Networks (VPNs) extend private networks across the Internet. They enable users to send and receive data across shared or public networks as if their computing devices were directly connected to the same private network~\cite{khanvilkar2004virtual}. The goal of CCVPN it to provide its users with the same functionality within the CCN Internet architecture. Therefore, the users can benefit from the features and security of a private network, even though the are not physically under the same private network.

In CCVPN, there are four main entities involved in the virtual private communication: \textit{Consumer}, \textit{Producer}, \textit{Consumer Side Gateway} ($G_c$), and \textit{Producer Side Gateway} ($G_p$). As in usual CCNs, the \textit{Consumer} is the network node that issues an interest for a given content (e.g., file, web page, video) that it wishes to retrieve. The Producer is the network node which originally created such content. $G_c$ and $G_p$ are the edge gateways responsible for ensuring the private communication among distinct domains. As we discuss later on, $G_c$ and $G_p$ can actually be implemented as a single network device, but we firstly present them as separate entities for the purpose of clarity.

\begin{figure*}[!ht]
\centering
\includegraphics[width=1.9\columnwidth]{images/architecture.pdf}
\caption{CCVPN connectivity architecture}
\label{fig:ccvpn}
\end{figure*}

As depicted in Fig.~\ref{fig:ccvpn}, the devices inside the \textit{Consumer} domain form a physically interconnected private network. Conversely, the devices in the \textit{Producer} domain also form a private network. Therefore, the goal is to create an overlay virtual network that unifies the \textit{Consumer} and the \textit{Producer} domains in way such that the original interests and contents are only visible to the devices inside these two domains. In other words, the interest $I_e$ and the content $C_e$, that are forwarded outside these domains, should give no information about the original interest $I_p$ and the actual content $C_p$.

In order to achieve such anonymous communication, $G_c$ is introduced in the \textit{Consumer} domain to encapsulate outgoing interests. Conversely, the $G_p$ is responsible for decapsulating the incoming encapsulated interests and forwarding them in their original form. When the content is forwarded back in response to the interest, $G_p$ encrypts the content before sending it outside the \textit{Producer} domain. Finally, $G_c$ decrypts the received content to its original form and forwards it back towards the \textit{Consumer}. Through the rest of this section we provide a detailed description on how such actions are implemented.

Upon the arrival of a new interest $I_p$, $G_c$ checks its Forwarding Information Base (FIB) to check if the interest prefix is in the list of prefixes for VPN communication. We assume that the FIB must be pre-configured with the list of prefixes which will trigger the VPN communication. Associated with such prefixes are $G_p$'s name and public key ($pk_e$). Therefore, if the prefix of $I_p$ is in the VPN prefixes list, $G_P$ runs Algorithm~\ref{alg:interestEncap} to generate a new interest $I_e$ which encapsulates the original interest $I_p$. Firstly, Algorithm~\ref{alg:interestEncap} generates a random symmetric key ($k_r$) which will be used later on to perform the \textit{Content} Encryption/Decryption. Next, it retrieves $G_p$'s name and public key from the FIB. It uses the public key to encrypt the symmetric key $k_r$ and the original interest $I_p$. Then it creates the new interest $I_e$ with $G_p$'s name as the interest name and the generated ciphertext as payload. Since $I_e$ has  the $G_p$'s name it will be routed towards $G_p$ and since the payload is singed with $G_p$'s public key, only $G_p$ can retrieve the original interest $I_p$ and the symmetric key $k_r$.

\begin{algorithm}[]\label{alg:interestEncap}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\Input{Original interest $I_p$;}
\Output{Encapsulated interest $I_e$;}
%$Ip_{name}$ = getName($I_p$)\\
%storeToPIT($Ip_{name}$)\\
$k_r$ = symmKeyGen();\\
$Gp_{name}$ = retrieveNameFromFIB($I_p$)\\
$pk_e$ = retrievePKFromFIB($I_p$)\\
$payload$ = $Enc_{pk_e}(I_p||k_r)$\\
$I_e$ = createNewInterest($Gp_{name}$, $payload$)\\
storeToPIT($I_e$,$k_r$)\\
\Return $I_e$;\\
\caption{Interest encapsulation (runs on $G_c$)}
\end{algorithm}

@@

\begin{algorithm}[]\label{alg:interestDecap}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\Input{ Encapsulated interest $I_e$;}
\Input{ Private key $sk_e$;}
\Output{Original interest $I_p$;}
$Ie_{name}$ = getName($I_e$)\\
$cipherText$ = getPayload($I_e$)\\
$I_p||k_r$ = $Dec_{sk_e}(cipherText)$\\
storeToPIT($I_p$,$k_r$,$Ie_{name}$)\\
\Return $I_p$;\\
\caption{Interest decapsulation (runs on $G_p$)}
\end{algorithm}

@@

\begin{algorithm}[]\label{alg:contentEnc}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\Input{Original content $C_p$;}
\Output{Encrypted content $C_e$;}
$name$ = getName($C_p$)\\
$k_r$ = retrieveKeyFromPIT($name$)\\
$Ie_{name}$ = retrieveNameFromPIT($name$)\\
$payload$ = $EncryptThenMAC_{k_r}(C_p)$\\
$C_e$ = createNewContent($Ie_{name}$,$payload$)\\
\Return $C_e$;\\
\caption{Content encryption  (runs on $G_p$)}
\end{algorithm}

Since $C_e$ and $I_e$ have the same name, $C_e$ will be forwarded all the way back to $G_c$. When $G_c$  receives $C_e$ $G_c$ will execute Algorithm~\ref{alg:contentDec}. It will match $C_e$'s name to the pending interest $I_e$ in its PIT, retrieving $k_r$. $k_r$ can then be used to verify the integrity of the received content and to decrypt it into the actual content $C_p$. After that, $C_p$ can be forwarded back to the \textit{Consumer}. If the MAC verification fails, it means that $C_e$ has been forged and $G_c$ ignores it.

\begin{algorithm}[]\label{alg:contentDec}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\Input{Encrypted content $C_e$;}
\Output{Original content $C_p$;}
$Ce_{name}$ = getName($C_e$)\\
$k_r$ = retrieveKeyFromPIT($Ce_{name}$)\\
$cipherText$ = getPayload($C_e$)\\
$C_p$ = Dec($k_r$,$cipherText$)\\
\eIf{$C_p$ == $\perp$}
    {
    \tcc{MAC verification failed}
    \Return ;\\
    }
    {\Return $C_p$;\\}
\caption{Content decryption (runs on $G_c$)}
\end{algorithm}

For clarity, we have defined a \textit{Consumer} and a \textit{Producer} domain. However, in reality, a single gateway can implement the functions of both $G_c$ and $G_p$. Therefore, consumers and producers can exist in both the domains and interests for contents can be issued from both sides. Also, it is worth to mention that, within the created CCVPNs, content caching would work just as it works in regular CCNs,  i.e., routers would be able to cache contents and respond to interests that were previously requested, enabling better resource usage and lower communication delays. Finally, we emphasize that $G_c$ encapsulation and decryption functions can also run inside the Consumer host. Conversely, $G_p$ can be implemented within the \textit{Producer} host. This enables its usage for one-to-one communication that would be completely anonymous to any  other entity in the network.

>>>>

\section{CCVPN Design}\label{metho}

Traditional Virtual Private Networks (VPNs) extend private networks across the Internet.
They enable users to send and receive data across shared or public networks as if their
computing devices were directly connected to the same private network~\cite{khanvilkar2004virtual}.
The goal of CCVPN it to provide its users with the same functionality within a CCN Internet architecture.
% Therefore, the users can benefit from the features and security of a private network, even though
% they are not physically under the same private network.

In CCVPN, there are four main entities involved in the virtual private communication: \textit{Consumer}, \textit{Producer}, \textit{Consumer Side Gateway} ($G_c$), and \textit{Producer Side Gateway} ($G_p$).
As usual in CCNs, the \textit{Consumer} is the network node that issues an interest for a given content
(e.g., file, web page, video) that it wishes to retrieve. The Producer is the network node which is
capable of providing such content. $G_c$ and $G_p$ are the edge gateways responsible for ensuring the
private communication among distinct domains. As we discuss later on, both $G_c$ and $G_p$ process can
run in a single gateway to enable bidirectional content service between two domains. However, we
firstly present them as separate entities for the purpose of clarity.

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{images/architecture.pdf}
\caption{CCVPN connectivity architecture}
\label{fig:ccvpn}
\end{figure}

As depicted in Fig.~\ref{fig:ccvpn}, the devices inside the \textit{Consumer} domain form a physically
interconnected private network. Conversely, the devices in the \textit{Producer} domain also form a
private network. Therefore, the goal is to create an overlay virtual network that unifies
the \textit{Consumer} and the \textit{Producer} domains in way such that the original interests
and contents are only visible to devices inside these two domains. In other words, the interest
$I_e$ and the content $C_e$, that are forwarded outside these domains, should give no information
about the original interest $I_p$ and the actual content $C_p$.

In order to achieve such private communication, $G_c$ is introduced in the \textit{Consumer} domain
to encapsulate outgoing interests. Conversely, $G_p$ is responsible for decapsulating the incoming
encapsulated interests and forwarding them in their original form. When the content is forwarded back
in response to the interest, $G_p$ encrypts the content before sending it outside the \textit{Producer}
domain. Finally, $G_c$ decrypts the received content to its original form and forwards it back towards
the \textit{Consumer}. Through the rest of this section, we provide a detailed description on how
such actions are implemented.

Upon the arrival of a new interest $I_p$, $G_c$ performs a lookup in its FIB to verify if the interest
prefix is in the list of prefixes for VPN communication. We assume that the FIB must be pre-configured
with the list of prefixes which will be tunnelled across the VPN, i.e, prefixes associated with the
producers inside of the Producer domain in Fig.~\ref{fig:ccvpn}. Associated with such prefixes
are $G_p$'s name and public key ($pk_e$). Therefore, if the prefix of $I_p$ is in the VPN prefixes
list, $G_P$ runs Algorithm~\ref{alg:interestEncap} to generate a new interest $I_e$ which encapsulates
the original interest $I_p$. Firstly, Algorithm~\ref{alg:interestEncap} generates a random symmetric
key ($k_r$) which will be used later on to perform the \textit{Content} Encryption/Decryption. Next,
it retrieves $G_p$'s name and public key from the FIB. It uses the public key to encrypt the
symmetric key $k_r$ and the original interest $I_p$. Then it creates the new interest $I_e$ with
$G_p$'s name as the interest name and the generated ciphertext as payload. Since $I_e$ has $G_p$'s name,
it will be routed towards $G_p$ and since the payload is singed with $G_p$'s public key, only $G_p$
can retrieve the original interest $I_p$ and the symmetric key $k_r$.

% \begin{framed}
\begin{algorithm}\label{alg:interestEncap}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\Input{Original interest $I_p$;}
\Output{Encapsulated interest $I_e$;}
%$Ip_{name}$ = getName($I_p$)\\
%storeToPIT($Ip_{name}$)\\
$k_r$ = symmKeyGen();\\
$Gp_{name}$ = retrieveNameFromFIB($I_p$)\\
$pk_e$ = retrievePKFromFIB($I_p$)\\
$payload$ = $Enc_{pk_e}(I_p||k_r)$\\
$I_e$ = createNewInterest($Gp_{name}$, $payload$)\\
storeToPIT($I_e$,$k_r$)\\
\Return $I_e$;\\
\caption{Interest encapsulation (runs on $G_c$)}
\end{algorithm}
% \end{framed}

@@

\begin{algorithm}\label{alg:interestDecap}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\Input{ Encapsulated interest $I_e$;}
\Input{ Private key $sk_e$;}
\Output{Original interest $I_p$;}
$Ie_{name}$ = getName($I_e$)\\
$cipherText$ = getPayload($I_e$)\\
$I_p||k_r$ = $Dec_{sk_e}(cipherText)$\\
storeToPIT($I_p$,$k_r$,$Ie_{name}$)\\
\Return $I_p$;\\
\caption{Interest decapsulation (runs on $G_p$)}
\end{algorithm}

@@

\begin{algorithm}\label{alg:contentEnc}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\Input{Original content $C_p$;}
\Output{Encrypted content $C_e$;}
$name$ = getName($C_p$)\\
$k_r$ = retrieveKeyFromPIT($name$)\\
$Ie_{name}$ = retrieveNameFromPIT($name$)\\
$payload$ = $EncryptThenMAC_{k_r}(C_p)$\\
$C_e$ = createNewContent($Ie_{name}$,$payload$)\\
\Return $C_e$;\\
\caption{Content encryption  (runs on $G_p$)}
\end{algorithm}

Since $C_e$ and $I_e$ have the same name, $C_e$ will be forwarded all the way back to $G_c$.
When $G_c$ receives $C_e$, $G_c$ will execute Algorithm~\ref{alg:contentDec}. It will match
$C_e$'s name to the pending interest $I_e$ in its PIT, retrieving $k_r$. $k_r$ can then be
used to verify the integrity of the received content and to decrypt it into the actual
content $C_p$. After that, $C_p$ can be forwarded back to the \textit{Consumer}. If the MAC
verification fails, it means that $C_e$ has been inadvertantly modified or tampered,
so $G_c$ discards it.

\begin{algorithm}\label{alg:contentDec}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\Input{Encrypted content $C_e$;}
\Output{Original content $C_p$;}
$Ce_{name}$ = getName($C_e$)\\
$k_r$ = retrieveKeyFromPIT($Ce_{name}$)\\
$cipherText$ = getPayload($C_e$)\\
$C_p$ = Dec($k_r$,$cipherText$)\\
\eIf{$C_p$ == $\perp$}
    {
    \tcc{MAC verification failed}
    \Return ;\\
    }
    {\Return $C_p$;\\}
\caption{Content decryption (runs on $G_c$)}
\end{algorithm}

For clarity, we have defined a \textit{Consumer} and a \textit{Producer} domain. However,
in reality, each of the two gateways would run both $G_c$ and $G_p$ processes. Therefore,
consumers and producers can exist in both the domains and interests for contents can be
issued from both sides. Also, it is worth to mention that, inside CCVPNs, content caching
would work just as it works in regular CCNs, i.e., routers would be able to cache content
and respond to interests that were previously requested, enabling better resource usage and
lower communication delays. Finally, we emphasize that $G_c$ encapsulation and decryption
functions can also run on Consumer host. Conversely, $G_p$ can be implemented within
the \textit{Producer} host. This enables private one-to-one, many-to-one, and one-to-many communication.

We also consider a slightly different version of CCVPN, in which we assume that $G_c$ and $G_p$
share a pre-installed symmetric key. The only difference in this version is that
Algorithm \ref{alg:interestEncap} uses symmetric key encryption instead of PKE to encapsulate
the original interest. Through the rest of this text, we refer to this variation as symmetric
key version of CCVPN.

### 2017-04-09 paper/05-sec-analysis.tex
Chris's pass

\subsection{System and Security Model}

Our security analysis considers the worst case scenario, in which the consumer issues an interest that has not been cached in any of the routers from the consumer nor producer domains. Therefore, the interest must traverse the whole network until reaching the content producer. Conversely, the content needs to be forwarded all the way back though the same path satisfying the routers' PIT entries. A system that is secure in this worst case is also secure when the content has been previously cached in some router along the way.

\textbf{Adversary Goals and Capabilities.} The goal of the adversary is either 1) to retrieve any information associated with the original issued interest $I_p$ and/or the original content $C_p$ or 2) to retrieve the identities of the consumer and/or producer, thus violating the anonymity in the communication. An adversary is also considered successful if it is able to impersonate the content producer by faking a content response. Since the original interest and the original content are visible inside the consumer and producer domains, we here assume that the adversary cannot eavesdrop or compromise hosts inside such domains. It is also worth to emphasize that, by the conceptual design of the VPN, communication is anonymous to hosts from outside the VPN but not to hosts that belong to that VPN. Anyhow, one-to-one anonymous communication is still achievable sing the VPN paradigm if the communication must be anonymous to any other host in the network. This also means that, as components of the producer and consumer domains, we assume that the gateways $G_c$ and $G_p$ cannot be compromised.

In our model the adversary is allowed to perform the following actions (when outside the consumer and producer domains):

\begin{itemize}
	\item \textbf{Eavesdrop and replay traffic:} An adversary can eavesdrop on a link learning among other things the packet contents and traffic patterns.
	\item \textbf{Deploy compromised routers or compromise existing routers:} An adversary is capable of deploying a compromised router ou compromised an existent router outside the VPN domains. By doing so the adversary becomes capable of maliciously injecting, delaying, altering, and dropping traffic. In addition, when an existing router is compromised, the adversary learns all of the private information contained in that router, such as private keys and cached content.
	\item \textbf{Deploy compromised caches:} As a consequence of the ability to compromise and deploy compromised routers, an adversary is also able to deploy compromised caches. This includes monitoring the routers' cache contents and replying with corrupted or fake data.
\end{itemize}

@@

Another use case for CCVPN is the traditional VPN use case, in which two physically separated local networks (for instances to offices of the same company in different countries) should virtually behave as a private local network. In that case, it is necessary to prevent that a given $G_c$, which is not part of that corporation's network to connect to $G_p$ and become part of the VPN. To that purpose, standard host-to-host CCN authentication mechanisms such as \cite{} can be used to authenticate $G_p$ and $G_c$ to each other. This must be performed before any VPN communication to make sure that only the appropriate parties are communicating under the CCVPN architecture. We leave the evaluation and specification of gateway-to-gateway authentication protocols as future work (see Sec.~\ref{sec:conclusion}).

@@

In this section we analyze the security of CCVPN. Our main security goal is
preventing an adversary from learning any information about the contents of
packets traversing a CCVPN tunnel. Formally, this translates into semantic
security of all traffic, modulo what can be inferred via traffic analysis.
A consequence of this property is that an off-path adversary, i.e., one that is
not in the consumer or producer domain, is unable to forge packets with
non-negligible probability. Our analysis relies on arguments in the standard
security model. It consists of assessing the security of the interest and
content encapsulation algorithms.

@@

\textit{\textbf{Proof--}} This follows directly from the definition of CCA-security and from the
same argument in the previous proof.

>>>>

\subsection{System and Security Model} \label{sec:goals}

Our security analysis considers the worst case scenario, in which the consumer issues an
interest that has not been cached in any of the routers from the consumer nor producer domains.
Therefore, the interest must traverse the entire network until reaching the producer.
Conversely, the content needs to be forwarded all the way back though the same path
satisfying the routers' PIT entries. A system that is secure in this worst case is also
secure when the content has been previously cached in some router along the way.

\textbf{Adversary Goals and Capabilities.} The goal of the adversary \adv\ is either 1) to
retrieve any information associated with the original issued interest $I_p$ and/or the
original content $C_p$ or 2) to retrieve the identities of the consumer and/or producer,
thus violating the anonymity in the communication. \adv\ is also considered successful
if it is able to impersonate the content producer by faking a content response. Since the
original interest and the original content are visible inside the consumer and producer
domains, we here assume that \adv\ cannot eavesdrop or compromise hosts inside
such domains. It is also worth to emphasize that, by the conceptual design of the VPN,
communication is anonymous to hosts from outside the VPN but not to hosts that belong to
that VPN. Anyhow, one-to-one anonymous communication is still achievable sing the VPN
paradigm if the communication must be anonymous to any other host in the network. This
also means that, as components of the producer and consumer domains, we assume that the
gateways $G_c$ and $G_p$ cannot be compromised.

In our model \adv\ is allowed to perform the following actions (when outside the consumer and producer domains):

\begin{itemize}
	\item \textbf{Eavesdrop and replay traffic:} \adv\ can eavesdrop on a link
    learning among other things the packet contents and traffic patterns.
	\item \textbf{Deploy compromised routers or compromise existing routers:} \adv\ is capable of
    deploying a compromised router ou compromised an existent router outside the VPN domains. By doing
    so \adv\ becomes capable of maliciously injecting, delaying, altering, and dropping traffic.
    In addition, when an existing router is compromised, \adv\ learns all of the private
    information contained in that router, such as private keys and cached content.
	\item \textbf{Deploy compromised caches:} As a consequence of the ability to compromise and
    deploy compromised routers, \adv\ is also able to deploy compromised caches. This
    includes monitoring the routers' cache contents and replying with corrupted or fake data.
\end{itemize}

@@

Another use case for CCVPN is the traditional VPN use case, in which two physically separated
local networks (for instance, offices of the same company in different countries) should virtually
behave as a private local network. In that case, it is necessary to prevent that a given $G_c$,
which is not part of that corporation's network to connect to $G_p$ and become part of the VPN.
To that purpose, standard host-to-host CCN authentication mechanisms can be used to authenticate
$G_p$ and $G_c$ to each other. This must be performed before any VPN communication, to make sure
that only the appropriate parties are communicating under the CCVPN architecture. We leave the
evaluation and specification of gateway-to-gateway authentication protocols as future work (see Sec.~\ref{sec:conclusion}).

@@

In this section we analyze the security of CCVPN. Our main security goal is
preventing \adv\ from achieving any of the goals outlined in Section \ref{sec:goals}.
Formally, this translates into semantic security of all traffic, modulo what can be inferred via traffic analysis.
A consequence of this property is that an off-path adversary, i.e., one that is
not in the consumer or producer domain, is unable to forge packets with
non-negligible probability. Our analysis relies on arguments in the standard
security model. It consists of assessing the security of the interest and
content encapsulation algorithms.

@@

\textit{\textbf{Proof (Sketch)--}} This follows directly from the definition of
CCA-security and from the same argument in the previous proof.
